---
title: "Getting Started with R"
author: "Your name here"
date: today
format: html
---

:::{.callout-note title="Goals"}
1. Load the packages we need
2. Load a data file
:::

If this document renders without errors, your setup works.

Click **Render** at the top of this pane to run everything. To run one chunk at
a time, click the green arrow at its top right.

Background reading:
[Experimentology, Appendix C](https://experimentology.io/102-rmarkdown.html).

## (1) Load packages

Run this once, by hand, if you have never installed these. It is set to
`eval: false` so it does not run every time you render.

```{r}
#| eval: false
install.packages(c("tidyverse", "here"))
```

```{r}
#| message: false
library(tidyverse)
library(here)
```

## (2) Load the data

`here()` builds file paths starting from the top of your project — the folder
holding `getting-started-with-r.Rproj`. That is why you open the project by
double-clicking the `.Rproj` file, and why you never need `setwd()`.

```{r}
here()
```

Paths built this way work on any computer, and keep working if you later move
this file into a subfolder.

```{r}
rt_data <- read_csv(here("data", "example_rt_data.csv"), show_col_types = FALSE)

glimpse(rt_data)
```

Simulated reaction times from a made-up Stroop-like task: `participant`,
`age_group` (child/adult), `condition` (congruent/incongruent), `rt_ms`, and
`accuracy` (1 = correct).

If you see 48 rows above, you are set up correctly.
